# Data transformation

The data is a .sav file, and data transformation is quite simple once the datasets are downloaded and put in the same folder. It is also necessary to install the package `haven` to read .sav file.

```{r}
library(haven)

dataset <- read_sav('dataset.sav')
```

We can take a peek at the dataset:

```{r}
head(dataset)
```

Each row is an individual response. To the individual is attached country, and answers to a number of multiple choice questions. Notice that there is also a `weight` column. Intructions from the source specify that answers must be weighted when used to compute the sum or mean response.

There is more nuanced, task-specific data transformation needed for different plots and tasks, which we introduce later. A general guideline for the data transformation codes later is that, one can use the `mutate` and `as_factor` function to create discrete versions of columns convenient for plotting. In particular, `as_factor` allows one to utilize the special <dbl+lbl> format of columns and allow graphs to output interpretable labels.